Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-15 paper.qmd
Removed unnecessary code
Added install packages if it's already not installed

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
library(quollr)
library(tibble)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(patchwork)
library(png)
library(colorspace)
library(kableExtra)
library(conflicted)

>>>>

```{r include=FALSE}
#| label: install-libraries
#| warning: false
#| echo: false

if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}

if (!requireNamespace("quollr", quietly = TRUE)) {
  remotes::install_github("JayaniLakshika/quollr")
}

if (!requireNamespace("tibble", quietly = TRUE)) {
  install.packages("tibble")
}

if (!requireNamespace("dplyr", quietly = TRUE)) {
  install.packages("dplyr")
}

if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}

if (!requireNamespace("readr", quietly = TRUE)) {
  install.packages("readr")
}

if (!requireNamespace("tidyr", quietly = TRUE)) {
  install.packages("tidyr")
}

if (!requireNamespace("patchwork", quietly = TRUE)) {
  install.packages("patchwork")
}

if (!requireNamespace("colorspace", quietly = TRUE)) {
  install.packages("colorspace")
}

if (!requireNamespace("kableExtra", quietly = TRUE)) {
  install.packages("kableExtra")
}

if (!requireNamespace("conflicted", quietly = TRUE)) {
  install.packages("conflicted")
}
```

```{r}
#| label: load-libraries
#| warning: false
#| echo: false
library(quollr)
library(tibble)
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(patchwork)
library(colorspace)
library(kableExtra)
library(conflicted)
